\input{prelude.tex}

\begin{document}

\setcounter{section}{-1}
\section{Prelude}

\begin{flushleft}
\textbf{How are the tasks rated?}
\end{flushleft}
\begin{flushright}
I want to say randomly, but they aren't. This is my own estimate of how I think
my students will perform based on their level and of the quality of the lecture
I've given previously. 5 stars are the exercises that will take them a
significant amount of time and may require external knowledge/research.
The one 1 stars easy and shouldn't take much effort at all. All the others lie 
somewhere inbetween on this range.
\end{flushright}

\begin{flushleft}
\textbf{I'm stuck! What next?}
\end{flushleft}
\begin{flushright}
Do let me know if some exercise made you seriously stumble. Take a break and
go for a walk, maybe try solve it tomorrow, perhaps you are tired. If you can't
crach that exercise to matter what be sure to inform me at the start of our
next lesson, we'll go through it.
\end{flushright}

\begin{flushleft}
\textbf{There is a builtin function (or a simple combination of those) that does
exactly what the task asks me to do, can I use it (them)?}
\end{flushleft}
\begin{flushright}
There for sure is and you may use it! Knowing your way around the standard library
is very important, however, you should only use the functions if you are sure
you could implement them yourself. You can \hbox{\s{list(set([1, 1, 2]))}} to 
keep only the unique elements, but can you do it with plain \s{for} loops? If 
that isn't the focus of the task you can take the shortcut, otheriwse reconsider.
\end{flushright}

\begin{flushleft}
\textbf{Why is the document so exquisitely formatted?}
\end{flushleft}
\begin{flushright}
I like it more that way. I am also practising \LaTeX\ in general,
it's really lovely.
\end{flushright}


\begin{flushleft}
\textbf{Hey, are you sure execrise X in section Y is correct?}
\end{flushleft}
\begin{flushright}
No I am not! Message me if you think there is a mistake since there very well might be one.
\end{flushright}

\tableofcontents

\section{Simple Stuff}
Prerequisites: control flow (branching, iteration), IO, arithmetic, atomic types.
\input{./lectures/lecture1/assignments.tex}

\section{Functions and Drawing}
Prerequisites: \s{turtle} module, lists, functions, recursion, induction.
\input{./lectures/lecture2/assignments.tex}

\clearpage
\doclicenseThis

\end{document}
